\fakebf{HIV virulence evolution in structured epidemic models}

### 2016-06-01 poster/hivlhs_eeid2016.Rnw
working on poster

\begin{block}{Sensitivity}
<<sens,dev="png",echo=FALSE,fig.width=20,fig.height=10,cache=TRUE,out.width="0.95\\textwidth">>=
mL3 <- subset(mL2,
       !((model=="implicit" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="random" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch+epc" &
          LHSvar %in% c("rho_base","c_u_ratio")) |
         (model=="pairform" &
          LHSvar %in% c("c_u_ratio","c_e_ratio"))))
## reorder factors
mL3$LHSvar <- factor(mL3$LHSvar,
                     levels=c("Beta1","Beta3",
                              "Duration1","Duration3",
                              "c_mean_base","c_e_ratio","rho_base",
                              "c_u_ratio"),
                     labels = c("beta[P]", "beta[D]", "D[P]", "D[D]",
                                "c", "c[e]/c[w]", "rho", "c[u]/c[w]"))

@@

ggplot(mL3,aes(LHSval,sumval,colour=model))+
    geom_point(pch=".",alpha=0.5)+
    facet_grid(sumvar~LHSvar,scales="free",
               labeller = L)+
    geom_smooth(se=FALSE)+labs(x="",y="")+
    ## leave a little extra room?
    scale_x_log10(expand=c(0,0.08),breaks=brkfun)+
    zero_margin
@
\end{block}
}
        \end{minipage}
    \end{beamercolorbox}

@@

\begin{itemize}
\item Random-mixing models best matched the most realistic models; extra-pair and uncoupled individuals washed out the effects
of epidemiological structure
\item Implicit models did worst
\item Variation among models (model structure) $\approx$ variation within models (parameter uncertainty)
\item Large differences
in evolutionary dynamics among different epidemiological models
$\to$ caution in predicting evolutionary responses
\item \textbf{neglected:} disease life history details, sex workers, age-structured mixing \dots
agent-based models?
\end{itemize}

>>>>

\begin{block}{Sensitivity}
\includegraphics[width=0.9\textwidth]{figure/sens-1.png}
<<sens,dev="png",echo=FALSE,fig.width=20,fig.height=10,cache=TRUE,out.width="0.95\\textwidth",eval=FALSE>>=
mL3 <- subset(mL2,
       !((model=="implicit" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="random" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch" &
          LHSvar %in% c("rho_base","c_u_ratio","c_e_ratio")) |
         (model=="instswitch+epc" &
          LHSvar %in% c("rho_base","c_u_ratio")) |
         (model=="pairform" &
          LHSvar %in% c("c_u_ratio","c_e_ratio"))))
## reorder factors
mL3$LHSvar <- factor(mL3$LHSvar,
                     levels=c("Beta1","Beta3",
                              "Duration1","Duration3",
                              "c_mean_base","c_e_ratio","rho_base",
                              "c_u_ratio"),
                     labels = c("beta[P]", "beta[D]", "D[P]", "D[D]",
                                "c", "c[e]/c[w]", "rho", "c[u]/c[w]"))

@@

ggplot(mL3,aes(LHSval,sumval,colour=model))+
    geom_point(pch=".",alpha=0.5)+
    facet_grid(sumvar~LHSvar,scales="free",
               labeller = L)+
    geom_smooth(se=FALSE)+labs(x="",y="")+
    ## leave a little extra room?
    scale_x_log10(expand=c(0,0.08),breaks=brkfun)+
    zero_margin
@
\begin{itemize}
\item {\small $\beta_{P,D}$: early/late-stage transmission probability; $D_{P,D}$: early/late-stage duration; $c$: partnership dissolution rate; $c_e/c_w$: extra- vs within-pair contact ratio; $\rho$: partnership formation rate; $c_u/c_w$: uncoupled contact rate ratio}
\end{itemize}
\end{block}
}
        \end{minipage}
    \end{beamercolorbox}

@@

\begin{itemize}
\item Random-mixing models best matched the most realistic models; extra-pair and uncoupled individuals washed out the effects
of epidemiological structure
\item Implicit models did worst
\item Variation among models (model structure) $\gtrsim$ variation within models (parameter uncertainty)
\item Large differences
in evolutionary dynamics among different epidemiological models
$\to$ caution in predicting evolutionary responses
\item \textbf{neglected:} disease life history details, sex workers, age-structured mixing \dots
agent-based models?
\end{itemize}
